---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-size: 18px;     
  line-height: 1.8;     
  font-family: "Helvetica", "Arial", sans-serif;  /* 
}

h1, h2, h3, h4 {
  font-weight: bold;
  margin-top: 1.5em;
}

```


## Screen Time Usage by App Type

This report presents the analysis of responses from my Google Form survey  "Daily Screen Time Usage by App Category".

**Visualizing App Usage Patterns by Age**

To explore the distribution of app usage time in screen usage by different age groups, I created two bar charts:

```{r}
library(tidyverse)
# Read survey response data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQMJW4Ho3DIrLIGQsABG6fAzj4zE1s8tgwoMEnSIIuIXslZMMTwgrFty0zqSkhCwBf9cNhalnNu9nW7/pub?output=csv")
# Rename the column data name to make it more tidy
latest_data <- rename(logged_data,
                      phone_type = 2,
                      most_used_app = 3,
                      usage_hours = 4,
                      peak_screen_time = 5,
                      app_type_before_18 = 6,
                      app_type_after_18 = 7,
                      age_group = 8)

# Take the median value of the time period to calculate the mean value of the peak_screen_numeric data
time_labels <- c("6--9am", "9--12", "12--15", "15--18", "18--21", "21--24", "after 24", "Not sure")
time_midpoints <- c(7.5, 10.5, 13.5, 16.5, 19.5, 22.5, 1, NA)
latest_data$peak_screen_numeric <- time_midpoints[match(latest_data$peak_screen_time, time_labels)]

mean_peak_time <- mean(latest_data$peak_screen_numeric, na.rm = TRUE)
min_time <- min(latest_data$usage_hours, na.rm = TRUE) 

# Draw a bar chart
latest_data %>%
  group_by(age_group) %>%
  summarise(avg_usage = mean(usage_hours, na.rm = TRUE)) %>%
  ggplot(aes(x = age_group, y = avg_usage, fill = age_group)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Usage Time of Most-Used App by Age Group",
    subtitle = "Comparing how long different age groups use their most-used app",
    caption = "Source: Jiayue's phone usage survey",
    x = "Age Group",
    y = "Average App Usage Time (hours)"
  )
```

### Dynamic Comments 1

In contrast, the age group with the lowest average usage is  `r latest_data %>% group_by(age_group) %>% summarise(avg = mean(usage_hours, na.rm = TRUE)) %>% arrange(avg) %>% slice(1) %>% pull(age_group)`,  
with only around  `r latest_data %>% group_by(age_group) %>% summarise(avg = mean(usage_hours, na.rm = TRUE)) %>% arrange(avg) %>% slice(1) %>% pull(avg) %>% round(1)` hours per day.

-----------------------------------------------------


```{r}
# Bar chart about peak time period of screen use
latest_data %>%
  count(peak_screen_time) %>%
  ggplot(aes(x = peak_screen_time, y = n, fill = peak_screen_time)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Distribution of Peak Screen Time",
    subtitle = "When do people use their phones the most?",
    caption = "Source: Jiayue's phone usage survey",
    x = "Peak Screen Time",
    y = "Number of Responses"
  )

```

### Dynamic Comments 2

The average peak screen time falls around `r round(mean_peak_time, 1)` o'clock, suggesting that most users are active in the evening.


